Case for Support

### 2021-11-12 caseForSupport.tex
Still in progress

Experimental control and neural data analysis are currently highly
disassociated.  Most neuroscientists collect their data and only afterward
analyze it. This split has had dramatic consequences for the progress of
neuroscience. First, most experimental control methods currently do not use
advanced data analysis methods to enhance their functionality. Second, the vast
majority of neural data analysis methods are offline and do not provide key
functionality needed for online experimental control. Using advanced data
analysis methods in experimental control will improve the sophistication of
experiments that are currently possible, and generate new demands for neural
data analysis methods that will generate advances in the field.

A central goal of the software resource proposed here is to address this
problem, by providing Bonsai~(an experimental control software ecosystem;
Figure~\ref{fig:bonsai} and Section~\ref{sec:bonsai}) with state-of-the-art
online (and offline) data analysis methods
(Figure~\ref{fig:proposedBonsaiExtensions} and
Section~\ref{sec:functionality}). Bonsai is
\textbf{unique} among experimental control software in that it allows people
with no programming experience to control sophisticated experiments. Its large
and rapidly growing user base demonstrates the need of this type of software
resources. With the proposed functionality to be added to Bonsai, its users
will be able to use sophisticated machine-learning methods to control their
experiments and analyze their data. This
\textbf{democratisation} of machine learning
functionality will allow scientists without computational skills to control
sophisticated experiments and analyze their data in unprecedented ways, which
will most probably yield important \textbf{advances in science}.

@@

Currently Bonsai has its own package manager, and its community of users have
already extended Bonsai's functionality with several contributed packages
(e.g., \ldots \textcolor{red}{Goncalo please reference the best contributed
packages developed by the Bonsai community}). However, these packages need to
be written in C\#, while most current neuroscience data analysis methods are
written in Python, R or Matlab. We propose to add to Bonsai capabilities to
communicate with software written in these languages
(Section~\ref{sec:bonsaiPythonMatlabCommunication}).  These capabilities will
allow a large number of neuroscience data analysis methods to be easily
integrated into the Bonsai ecosystem and will provide Bonsai users a large
repertoire of advance machine learning methods for their behavioral and neural
data analysis.

Developers of advanced data-analysis methods should become interested in
integrating them into de Bonsai ecosystem, which will allow their methods to
reach the wide Bonsai community. In addition this integration will enable
method developers, to easily compare the performance of their methods with
that of many methods previously integrated into the Bonsai ecosystem. Method
developers will thus become a new type of Bonsai users, which will contribute
to the \textbf{sustainability} of the proposed resource beyond the period of
BBSRC-BBR funding.

Using the proposed capabilities to communicate Bonsai with software written in
other languages, we will integrate into Bonsai an initial set of state-of-the
art behavioral and neural data analysis methods
(Section~\ref{sec:functionality}).

@@

Bonsai~\citep{lopesEtAl15,lopesAndMonteiro21} is a free and open-source visual
programming language that emphasizes performance, flexibility, and ease-of-use,
allowing scientists with no previous programming experience to quickly develop
their own high-performance data acquisition and experimental control systems
(Figure 1c). Bonsai combines a high-level event algebra for data streams with
an integrated development environment (IDE) and a strong library of plugins
supporting multiple hardware and software packages used by the biomedical
research community (Figures 1a, 1b).

Bonsai has a large user base in the systems neuroscience community.
Quantifications of this user base are provided in Figures 1d-1f.  In the last
year alone, we estimate more than 1,000 new users have started to incorporate
Bonsai into their experimental protocols across the world. The surprising rate
of adoption of Bonsai in non-programmer experimental labs highlights the need
for accessible programming tools that enable state-of-the-art technology but
also allow researchers to stay in control and change their experimental
paradigms.  Many open-source software tools are either inaccessible to
non-programmers, or too constrained to be of general use outside their narrow
domain of application. Bonsai has been successful because it has straddled this
gap to some extent.

@@

We intend to improve an \textbf{existing resource}, the Bonsai ecosystem. We
propose to create software infrastructure to facilitate the integration into it
of existing advanced data analysis methods
(Section~\ref{sec:softwareInfrastructure}).
%
To demonstate the use of this infrastructure, and to provide Bonsai users with
an initial set of advanced machine intelligence neural data analysis methods,
we will add to the Bonsai ecosystem machine learning functionality to control
neuroscience experiments and to analyze data generated by them
(Section~\ref{sec:functionality}).

This initial set of methods should demonstrate to Bonsai users, and to
machine-learning methods developers, the potential of embedding
machine-learning functionality into the experimental control loop. We propose
user engagement activities to expose both of these groups of people to this
potential (Section~\ref{sec:userEngagement}).  When data-analysis method
developers recognize this potentials, they will become interested in
contributing their methods to the Bonsai ecosystem, ensuring the
\textbf{long-term sustainability} of the proposed resource.

@@

\begin{comment}
Bonsai does not currently provide machine learning functionality. For instance,
the close-loop experimental control depicted in
Figure~\ref{fig:bci} cannot be currently implemented in
Bonsai. It represents the control of an experiment where a subject guides the
mouse position in a computer screen with her brain activity (Section~\ref{}).
Nodes highlighted in color require machine intelligence functionality currently
not available in Bonsai.
%
\end{comment}

@@

\begin{comment}
    The spike detector transforms membrane
potentials into spike sequences. The spike sorter transforms spikes squences
into lists of spikes, one list per neuron. The latents extractor transforms
multi-neuron lists of spikes into latent trajectories summarizing the
multi-neuon spiking activity.  The neural decoder predicts the next cursor
position from the latent trajectories.
\end{comment}

\begin{comment}
middl, whose output will set
As in this library,
there will be three type of machine intelligence operators in Bonsai:
%
estimator operators for building and fitting models, predictor operators for
making predictions and transformer operators for converting data. These
operators will be implemented by objects exposing the corresponding interfaces.

@@

The predictor interface extends the notion of an estimator by adding a predict
method that takes an array X\_test and produces predictions for X\_test, based
on the learned parameters of the estimator (we call the input to predict
“X\_test” in order to emphasize that predict generalizes to new data). In the
case of supervised learning estimators, this method typically returns the
predicted labels or values computed by the model.

@@

Using the previous software, we will build C\# wrappers around machine
intellgence programs written in other languages, so that these programs
implement the Estimator, Predictor or Transformer interfaces and can be
integrated into Bonsai as machine intelligence operators.

@@

We propose to initially add to Bonsai machine intelligence functionality to
support neuroscience experiments because, currently, neuroscience is the
research area with the largest number of Bonsai users. Within neuroscience, we
propose to add functionality for video-based behavioral analysis
(Section~\ref{sec:videoBasedBehavioralAnalysis}) and for running
brain-computer-interface experiments (Section~\ref{sec:bci}), since these tasks
are relevant to many Bonsai users, and recent advances in machine learning
will greatly improve their implementation in Bonsai.

@@

Precisely quantifying animal behavior is an essential step toward understanding
brain function.  Deeplabcut is a Python-based software for tracking animal body
parts \citep{mathisEtAl18}, which it is currently well integrated with
Bonsai~\citep{kaneEtAl20}. Here we propose extensions to Bonsai to extract
other informative features from video recordings.

@@

    \item[Motion sequencing]\citep[MoSeq;][]{wiltschkoEtAl15}: extracts patterns
        of behavior that repeat over time (i.e., syllables of behavior) from
        video data. For instance, it parses (in an unsupervised way) the
        behavior of a mouse in an arena into segments of time where a mouse
        was running, rearing and grooming. It uses a hidden Markov model and it
        is implemented in Python\footnote{Code for MoSeq can be requested from
        the Datta laboratory, as indicated at
        \href{http://datta.hms.harvard.edu/research/behavioral-analysis/}{http://datta.hms.harvard.edu/research/behavioral-analysis/}.}.
        After trained MoSeq can be used to detect behavioral syllables online.

    \item[Decoding behavior from neural
        activity]\citep[BehaveNet;][]{battyEtAl19} combines hidden Markov
        models with convolutional autoencoders and discriminative models to
        decode video data from neural recordings. It is implemented in
        Python\footnote{\href{https://github.com/themattinthehatt/behavenet}{https://github.com/themattinthehatt/behavenet}}.
        After trained it can be used online to decode video data and detect
        behavioral syllables.

@@

    \item[Gaussian Linear Dynamical
        System]\citep[GLDS;][]{andersonAndMoore12}: with sufficiently large
        bin sizes, spike counts can be modeled as Gaussian random processes.
        This Gaussianity assumption greatly simplifies the estimation of
        parameters of linear dynamical system (LDS) models, as well as
        inferences about their states. After models parameters have been
        learned, GLDS can be used online. A unique feature of GLDS is that the
        posterior distribution of states given all observation up to the
        present can be calculated efficiently. This estimate of the posterior
        distribution can be used online for experimental control, as we
        propose in Section~\ref{sec:comparisonOfMultipleMethods}. We will use an R implementation of GLDS
        which allows the use of external
        inputs\footnote{\href{https://github.com/joacorapela/kalmanFilter}{https://github.com/joacorapela/kalmanFilter}}.

    \item[Poisson Linear Dynamical System]\citep[PLDS;][]{mackeEtAl15}: for
        smaller bin sizes, spike counts are better modeled as Poisson random
        processes, rather than Gaussian ones. The algorithm described in
        \citet{mackeEtAl15} can estimate the parameters of a LDS, and make
        inferences about its states, from Poisson distributed observations.  We
        propose to interface Bonsai with a Matlab implementation of
        PLDS\footnote{\href{https://bitbucket.org/mackelab/pop\_spike\_dyn/src/master/}{https://bitbucket.org/mackelab/pop\_spike\_dyn/src/master/}}
        that uses variational inference. PLDS does not provide online estimates
        of the states, since data from a full trial is needed for state
        inference.

@@

Spikes are extracted from a higher-frequency range of extracellulary recorded
voltages. Local field potentials (LFPs) are computed from a lower-frequency
range and are another important signal to understand brain function. We propose
to use states inferred from LFPs by GLDS, GPFA, HMM and LFADS
(Section~\ref{sec:lowDimensionalRepresentationsOfSpikingData}) as
low-dimensional representations of the LFP.

@@

In order to use low-dimensional representations of spiking activity and/or of
LFPs to guide the control of experiments, we need a decoder to optimally map
these low-dimensional representations to experimental controls.
%
We propose to implement in Bonsai several decoding/classification algorithms:
k-nearest neighbor, linear discriminative analysis, support vector machines,
random forests, artificial neural networks, naive Bayes and Gaussian process
classifiers.

@@

We propose to add functionality to Bonsai to facilitate multi-method
comparisons in user-supplied datasets. Below we describe a comparison that we
will perform in Bonsai to asses the relative performance of the methods
described in the previous sections with neural recordings from behaving rats.
These recordings are currently being performed, to address scientific questions,
at the laboratory of Prof.~Akrami in the SWC.
%
Details of the experimental task appear in~\citet{akramiEtAl18}.
%
Briefly, in this task there are three nose ports (left, center, right). Rats
initiate a trial by inserting their nose in the center port for the duration of
the fixation period, until they hear a Go stimulus. During the fixation period
two stimuli $s_a$ and $s_b$ are presented. Rats should decide which stimuli is
louder. If $s_a$ is louder than $s_b$ the correct action is to poke the nose
into the right port in order to collect a liquid reward, and if $s_b$ is louder
than $s_a$ the correct choice is the left port.

@@

To assess the progress of the proposed project, we propose the following
measurable targets:

@@

    \item[implementation of software infrastructure]
        (Section~\ref{sec:softwareInfrastructure}) includes the
        implementation of the machine abstractions described in Section~\ref{}
        and of the capabilities to be added to Bonsai to communicate with
        software written in other languages described in Section~\ref{}. We
        will consider this target completed when we can implement a simple BCI
        application, with the architecture depicted in Figure~\ref{}, with
        machine learning functionality provided by software in Python, Matlab
        and R.

    \item[implementation of functionality] (Sections~\ref{sec:functionality})
        includes the integration into Bonsai of machine learning software
        for video-based behavioral analysis (Section~\ref{}) and for
        brain-computer-interface applications (Section~\ref{}). Completion of
        this target requires that Bonsai can perform these tasks interacting
        with software written in other languages.

@@

    \item method developers integrate their methods into the Bonsai ecosystem.
        The integration of machine learning functionality into Bonsai will use
        Bonsai's package manager. We propose to use this package manaer to tack
        the number of machine intelligence methods integrated into Bonsai.

>>>>

Experimental control and neural data analysis are currently highly
disassociated.  Most neuroscientists collect their data and only after ward
analyse it. This split has had dramatic consequences for the progress of
neuroscience. First, most experimental control methods currently do not use
advanced data analysis methods to enhance their functionality. Second, the vast
majority of neural data analysis methods are offline and do not provide key
functionality needed for online experimental control. Using advanced data
analysis methods in experimental control will improve the sophistication of
experiments that are currently possible, and generate new demands for neural
data analysis methods that will trigger advanced in machine learning.

A central goal of the software resource proposed here is to address this
problem, by providing Bonsai~(an experimental control software ecosystem;
Figure~\ref{fig:bonsai} and Section~\ref{sec:bonsai}) with state-of-the-art
online (and offline) data analysis methods
(Figure~\ref{fig:proposedBonsaiExtensions} and
Section~\ref{sec:functionality}). Bonsai is
\textbf{unique} among experimental control software in that it allows people
with no programming experience to control sophisticated experiments. Its large
and rapidly growing user base demonstrates the need of this type of software
resources. With the proposed functionality to be added to Bonsai, its users
will be able to use sophisticated machine-learning methods to control their
experiments and analyse their data. This
\textbf{democratisation} of machine learning
functionality will allow scientists without computational skills to control
sophisticated experiments and analyse their data in unprecedented ways, which
will most probably yield important \textbf{advances in science}.

@@

Currently Bonsai has its own package manager, and its community of users have
already extended Bonsai's functionality with several contributed packages
(e.g., \ldots \textcolor{red}{Goncalo please reference the best contributed
packages developed by the Bonsai community}). However, these packages need to
be written in C\#, while most current neuroscience data analysis methods are
written in Python, R or Matlab. We propose to add to Bonsai capabilities to
communicate with software written in these languages
(Section~\ref{sec:bonsaiPythonMatlabCommunication}).  These capabilities will
allow a large number of neuroscience data analysis methods to be easily
integrated into the Bonsai ecosystem and will provide Bonsai users a large
repertoire of advance machine learning methods for their behavioural and neural
data analysis.

Developers of advanced data-analysis methods should become interested in
integrating them into the Bonsai ecosystem, which will allow their methods to
reach the wide Bonsai community. In addition this integration will enable
method developers, to easily compare the performance of their methods with
that of many methods previously integrated into the Bonsai ecosystem. Method
developers will thus become a new type of Bonsai users, which will contribute
to the \textbf{sustainability} of the proposed resource beyond the period of
BBSRC-BBR funding.

Using the proposed capabilities to communicate Bonsai with software written in
other languages, we will integrate into Bonsai an initial set of state-of-the
art behavioural and neural data analysis methods
(Section~\ref{sec:functionality}).

@@

Bonsai~\citep{lopesEtAl15,lopesAndMonteiro21} is a free and open-source visual
programming language that emphasises performance, flexibility, and ease-of-use,
allowing scientists with no previous programming experience to quickly develop
their own high-performance data acquisition and experimental control systems
(Figure 1c). Bonsai combines a high-level event algebra for data streams with
an integrated development environment (IDE) and a strong library of plugins
supporting multiple hardware and software packages used by the biomedical
research community (Figures 1a, 1b).

Bonsai has a large user base in the systems neuroscience community.
Quantification of this user base are provided in Figures 1d-1f.  In the last
year alone, we estimate more than 1,000 new users have started to incorporate
Bonsai into their experimental protocols across the world. The surprising rate
of adoption of Bonsai in non-programmer experimental labs highlights the need
for accessible programming tools that enable state-of-the-art technology but
also allow researchers to stay in control and change their experimental
paradigms.  Many open-source software tools are either inaccessible to
non-programmers, or too constrained to be of general use outside their narrow
domain of application. Bonsai has been successful because it has straddled this
gap to some extent.

@@

We intend to improve an \textbf{existing resource}, the Bonsai ecosystem. We
propose to create software infrastructure to facilitate the integration into it
of existing advanced data analysis methods
(Section~\ref{sec:softwareInfrastructure}).
%
To demonstrate the use of this infrastructure, and to provide Bonsai users with
an initial set of advanced machine intelligence neural data analysis methods,
we will add to the Bonsai ecosystem machine learning functionality to control
neuroscience experiments and to analyse data generated by them
(Section~\ref{sec:functionality}).

This initial set of methods should demonstrate to Bonsai users, and to
machine-learning methods developers, the potential of embedding
machine-learning functionality into the experimental control loop. We propose
user engagement activities to expose both of these groups of people to this
potential (Section~\ref{sec:userEngagement}).  When data-analysis method
developers recognise this potentials, they will become interested in
contributing their methods to the Bonsai ecosystem, ensuring the
\textbf{long-term sustainability} of the proposed resource.

Adding machine learning functionality to the experimental control loop will
make possible the implementation of experiments with unprecedented levels of
control. Moreover, equipping experimental scientists without programming
experience with machine learning tools will considerably increase the
application of machine learning to the biosciences, which most probably will
translate into groundbreaking scientific discoveries.

@@

\begin{comment}
Bonsai does not currently provide machine learning functionality. For instance,
the close-loop experimental control depicted in
Figure~\ref{fig:bci} cannot be currently implemented in
Bonsai. It represents the control of an experiment where a subject guides the
mouse position in a computer screen with her brain activity (Section~\ref{}).
Nodes highlighted in colour require machine intelligence functionality currently
not available in Bonsai.
%
\end{comment}

@@

\begin{comment}
    The spike detector transforms membrane
potentials into spike sequences. The spike sorter transforms spikes sequences
into lists of spikes, one list per neuron. The latents extractor transforms
multi-neuron lists of spikes into latent trajectories summarising the
multi-neuron spiking activity.  The neural decoder predicts the next cursor
position from the latent trajectories.
\end{comment}

\begin{comment}
middle, whose output will set
As in this library,
there will be three type of machine intelligence operators in Bonsai:
%
estimator operators for building and fitting models, predictor operators for
making predictions and transformer operators for converting data. These
operators will be implemented by objects exposing the corresponding interfaces.

@@

The predictor interface extends the notion of an estimator by adding a predict
method that takes an array X\_test and produces predictions for X\_test, based
on the learned parameters of the estimator (we call the input to predict
“X\_test” in order to emphasise that predict generalises to new data). In the
case of supervised learning estimators, this method typically returns the
predicted labels or values computed by the model.

@@

Using the previous software, we will build C\# wrappers around machine
intelligence programs written in other languages, so that these programs
implement the Estimator, Predictor or Transformer interfaces and can be
integrated into Bonsai as machine intelligence operators.

@@

We propose to initially add to Bonsai machine intelligence functionality to
support neuroscience experiments because, currently, neuroscience is the
research area with the largest number of Bonsai users. Within neuroscience, we
propose to add functionality for video-based behavioural analysis
(Section~\ref{sec:videoBasedBehavioralAnalysis}) and for running
brain-computer-interface experiments (Section~\ref{sec:bci}), since these tasks
are relevant to many Bonsai users, and recent advances in machine learning
will greatly improve their implementation in Bonsai.

@@

Precisely quantifying animal behaviour is an essential step toward understanding
brain function.  Deeplabcut is a Python-based software for tracking animal body
parts \citep{mathisEtAl18}, which it is currently well integrated with
Bonsai~\citep{kaneEtAl20}. Here we propose extensions to Bonsai to extract
other informative features from video recordings.

@@

    \item[Motion sequencing]\citep[MoSeq;][]{wiltschkoEtAl15}: extracts patterns
        of behaviour that repeat over time (i.e., syllables of behaviour) from
        video data. For instance, it parses (in an unsupervised way) the
        behaviour of a mouse in an arena into segments of time where a mouse
        was running, rearing and grooming. It uses a hidden Markov model and it
        is implemented in Python\footnote{Code for MoSeq can be requested from
        the Datta laboratory, as indicated at
        \href{http://datta.hms.harvard.edu/research/behavioral-analysis/}{http://datta.hms.harvard.edu/research/behavioral-analysis/}.}.
        After trained MoSeq can be used to detect behavioral syllables online.

    \item[Decoding behaviour from neural
        activity]\citep[BehaveNet;][]{battyEtAl19} combines hidden Markov
        models with convolutional autoencoders and discriminative models to
        decode video data from neural recordings. It is implemented in
        Python\footnote{\href{https://github.com/themattinthehatt/behavenet}{https://github.com/themattinthehatt/behavenet}}.
        After trained it can be used online to decode video data and detect
        behavioral syllables.

@@

    \item[Gaussian Linear Dynamical
        System]\citep[GLDS;][]{andersonAndMoore12}: with sufficiently large
        bin sizes, spike counts can be modelled as Gaussian random processes.
        This Gaussianity assumption greatly simplifies the estimation of
        parameters of linear dynamical system (LDS) models, as well as
        inferences about their states. After models parameters have been
        learned, GLDS can be used online. A unique feature of GLDS is that the
        posterior distribution of states given all observation up to the
        present can be calculated efficiently. This estimate of the posterior
        distribution can be used online for experimental control, as we
        propose in Section~\ref{sec:comparisonOfMultipleMethods}. We will use an R implementation of GLDS
        which allows the use of external
        inputs\footnote{\href{https://github.com/joacorapela/kalmanFilter}{https://github.com/joacorapela/kalmanFilter}}.

    \item[Poisson Linear Dynamical System]\citep[PLDS;][]{mackeEtAl15}: for
        smaller bin sizes, spike counts are better modelled as Poisson random
        processes, rather than Gaussian ones. The algorithm described in
        \citet{mackeEtAl15} can estimate the parameters of a LDS, and make
        inferences about its states, from Poisson distributed observations.  We
        propose to interface Bonsai with a Matlab implementation of
        PLDS\footnote{\href{https://bitbucket.org/mackelab/pop\_spike\_dyn/src/master/}{https://bitbucket.org/mackelab/pop\_spike\_dyn/src/master/}}
        that uses variational inference. PLDS does not provide online estimates
        of the states, since data from a full trial is needed for state
        inference.

@@

Spikes are extracted from a higher-frequency range of extracellularly recorded
voltages. Local field potentials (LFPs) are computed from a lower-frequency
range and are another important signal to understand brain function. We propose
to use states inferred from LFPs by GLDS, GPFA, HMM and LFADS
(Section~\ref{sec:lowDimensionalRepresentationsOfSpikingData}) as
low-dimensional representations of the LFP.

@@

In order to use low-dimensional representations of spiking activity and/or of
LFPs to guide the control of experiments, we need a decoder to optimally map
these low-dimensional representations to experimental controls.
%
We propose to implement in Bonsai several decoding/classification algorithms:
k-nearest neighbour, linear discriminative analysis, support vector machines,
random forests, artificial neural networks, naive Bayes and Gaussian process
classifiers.

@@

We propose to add functionality to Bonsai to facilitate multi-method
comparisons in user-supplied datasets. Below we describe a comparison that we
will perform in Bonsai to asses the relative performance of the methods
described in the previous sections with neural recordings from behaving rats.
These recordings are currently being performed, to address scientific questions,
at the laboratory of Prof.~Akrami in the SWC.
%
Details of the experimental task appear in~\citet{akramiEtAl18}.
%
Briefly, in this task there are three nose ports (left, centre, right). Rats
initiate a trial by inserting their nose in the centre port for the duration of
the fixation period, until they hear a Go stimulus. During the fixation period
two stimuli $s_a$ and $s_b$ are presented. Rats should decide which stimuli is
louder. If $s_a$ is louder than $s_b$ the correct action is to poke the nose
into the right port in order to collect a liquid reward, and if $s_b$ is louder
than $s_a$ the correct choice is the left port.

@@

We propose to assess the progress of the proposed project using the following
measurable targets:

@@

    \item[implementation of software infrastructure]
        (Section~\ref{sec:softwareInfrastructure}) includes the
        implementation of the machine abstractions, described in
        Section~\ref{},
        and of the capabilities to allow Bonsai communicate with
        software written in other languages, described in Section~\ref{}. We
        will consider this target completed when we can implement a simple BCI
        application, with the architecture depicted in Figure~\ref{}, with
        machine learning functionality provided by software in Python, Matlab
        and R.

    \item[implementation of functionality] (Sections~\ref{sec:functionality})
        includes the integration into Bonsai of machine learning software for
        video-based behavioral analysis (Section~\ref{}) and for
        brain-computer-interface applications (Section~\ref{}). Completion of
        this target requires that Bonsai can perform each of these tasks
        separately, in conjunction with software written in Python, R and
        Matlab.

@@

    \item method developers integrate their methods into the Bonsai ecosystem.
        The integration of machine learning functionality into Bonsai will use
        Bonsai's package manager. We propose to use this package manager to tack
        the number of machine intelligence methods integrated into Bonsai.
